---
title: "Model Selection_Revised"
author: "Vineed"
date: "3/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(ISLR)
fix(Hitters)

sum(is.na(Hitters))

Hitters <- na.omit(Hitters)

library(leaps)

best.model <- regsubsets(Salary~., data = Hitters, nvmax = ncol(Hitters))

summary(best.model)

best.model.summary <- summary(best.model)
names(best.model.summary)

best.model.summary$rsq
plot(best.model.summary$adjr2)
```
All the below points are made with summary object

```{r}
par(mfrow = c(2,2))

plot(best.model.summary$rss, xlab = "No. of Variables", 
     ylab = "RSS", type = "l")
which.min(best.model.summary$rss)
points(19,best.model.summary$rss[19], col = "red", pch = 19, cex = 1)

plot(best.model.summary$adjr2,xlab = "No. of Variables", 
     ylab = "Adj. Rsq", type = "l" )
which.max(best.model.summary$adjr2)
points(11,best.model.summary$adjr2[11], col = "red", pch = 19, cex = 1)

plot(best.model.summary$bic, xlab = "No. of Variables", ylab = "BIC",
     type = 'l')
which.min(best.model.summary$bic)
points(6,best.model.summary$bic[6], col = "red", pch = 19, cex = 1)

plot(best.model.summary$cp, xlab = "No. of Variables", ylab = "Cp",
     type = 'l')
which.min(best.model.summary$cp)
points(10,best.model.summary$cp[10], col = "red", pch = 19, cex = 1)
```

We can use the plot objects in the model developed as shown below
```{r}
plot(best.model, scale = "r2")
plot(best.model, scale = "adjr2")
plot(best.model, scale = "bic")
plot(best.model, scale = "Cp")
```
To get coeffients of a model with a certain number of variables, the following function can be used.

```{r}

coef(best.model,8)

```
Forward and Backward Subset
__________________________

```{r}
regfit.forward <- regsubsets(Salary~., data = Hitters, 
                             nvmax = ncol(Hitters), method = "forward")

regfit.backward <- regsubsets(Salary~., data = Hitters,
                              nvmax = 20, method = "backward")

summary(regfit.forward)
```
Now, we will use cross validation methods to estimate test error and subsequently identify the best model

```{r}

set.seed(1)
train <- sample(263, 180)
regfit.best <- regsubsets(Salary~., data = Hitters[train,],
                          nvmax = 20)
test.mat <- model.matrix(Salary~., data = Hitters[-train,])

val.errors <- rep(NA, 19)
for (i in 1:19){
  coefi <- coef(regfit.best,id = i)
  pred <- test.mat[,names(coefi)]%*%coefi
  val.errors[i] <- mean((Hitters$Salary[-train]-pred)^2)
  
}

which.min(val.errors)

coef(regfit.best,11)

```
Since there is no predict() in regsubsets, we are making our own


```{bash}
predict.regsubsets <- function(object, newdata, id...){
form <- as.formula(object[[2]])
mat <- model.matrix(form,newdata)
coefi <- coef(object, id)
xvars = names(coefi)
mat[,xvars]%*%ceofi
}



```

